Automated neuroimaging data management with the Sea filesystem

### 2021-10-08 paper/paper_neuro.tex
typos

\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\algblock{Input}{EndInput}
\algnotext{EndInput}
\algblock{Output}{EndOutput}
\algnotext{EndOutput}
\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}: #1}}}

@@

    Neuroimaging workflows, particularly preprocessing ones, may lead to a magnification in output sizes due to <add reason>. They also produce
    significant amounts of intermediary data due to being composed of a multitude of steps. 
\end{abstract}
}

@@

HPC systems rely on scalable network-based parallel filesystems (e.g. Lustre) for storage. While such file
systems offer excellent performance, they are shared between all the users on the cluster. Meaning that users
with data-intensive can effectively deteriorate the performance of the shared file system for all users on
the cluster. Solutions for improving shared file system performance include throttling the data intensive workloads
or recommending the use of Burst Buffers~\cite{bb} (e.g. reserving a compute node for storage or leveraging
local compute storage during processing). The latter, however, requiring that the user manages their data to
and from the Burst Buffer.

@@

As neuroimaging pipeline results are typically required post-processing and HPC compute-local resources are only accessible during the
reserved duration, Sea provides functionality to flush and evict data to persistent shared storage. This is accomplished via a separate
thread (known as the ``flusher'') that moves data from the caches to long-term storage. A separate thread is used, in this case, to avoid
interrupting on going processing with data management operations.
Users must inform Sea of files that need to be
persisted to storage within a file called \texttt{.sea\_flushlist}, and temporary files which can be removed from cache within a file
called the \texttt{.sea\_evictlist}. Both these files can be populated using regular expressions to denote the paths to flush and evict.
If a file occurs in both the \texttt{.sea\_flushlist} and \texttt{.sea\_evictlist}, Sea will interpret this as a \texttt{move} operation
and simply move the file from local to persistent storage rather than copying it. Files that will be reused by the application should only
be flushed rather than flushed and evicted, as files can benefit from speedups related to reading from fast rather than slow storage.
Sea currently also provides a rudimentary prefetch thread that can move files located within the Sea filesystem to the fastest available cache.
To use Sea's prefetch capabilities, a file called \texttt{.sea\_prefetchlist} needs to be populated using regular expressions like the
flushing and eviction files.

>>>>

\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\algblock{Input}{EndInput}
\algnotext{EndInput}
\algblock{Output}{EndOutput}
\algnotext{EndOutput}
\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:} #1\color{black}\xspace}
\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}: #1}}}

@@

    Neuroimaging workflows, particularly preprocessing ones, may lead to a magnification in output sizes due to the presence of multiple intermediary processing steps. They also produce
    significant amounts of intermediary data due to being composed of a multitude of steps. 
\end{abstract}
}

@@

HPC systems rely on scalable network-based parallel filesystems (e.g. Lustre) for storage. While such file
systems offer excellent performance, they are shared between all the users on the cluster. Meaning that users
with data-intensive analyses can effectively deteriorate the performance of the shared file system for all users on
the cluster. Solutions for improving shared file system performance include throttling the data intensive workloads
or recommending the use of Burst Buffers~\cite{bb} (e.g. reserving a compute node for storage or leveraging
local compute storage during processing). The latter, however, requiring that the user manages their data to
and from the Burst Buffer.

@@

As neuroimaging pipeline results typically require post-processing and HPC compute-local resources are only accessible during the
reserved duration, Sea provides functionality to flush and evict data to persistent shared storage. This is accomplished via a separate
thread (known as the ``flusher'') that moves data from the caches to long-term storage. A separate thread is used, in this case, to avoid
interrupting on going processing with data management operations.
Users must inform Sea of files that need to be
persisted to storage within a file called \texttt{.sea\_flushlist}, and temporary files which can be removed from cache within a file
called the \texttt{.sea\_evictlist}. Both these files can be populated using regular expressions to denote the paths to flush and evict.
If a file occurs in both the \texttt{.sea\_flushlist} and \texttt{.sea\_evictlist}, Sea will interpret this as a \texttt{move} operation
and simply move the file from local to persistent storage rather than copying it. Files that will be reused by the application should only
be flushed rather than flushed and evicted, as files can benefit from speedups related to reading from fast rather than slow storage.
Sea currently also provides a rudimentary prefetch thread that can move files located within the Sea filesystem to the fastest available cache.
To use Sea's prefetch capabilities, a file called \texttt{.sea\_prefetchlist} needs to be populated using regular expressions like the
flushing and eviction files.
